### 2020-08-24 code/figureSM1.Rmd
Update chunk code name in SM1

```{r figure-2-plot, fig.width = 9}
load("../data/figure1B_data.rda") ## Load in data processed in figure1.Rmd
load("../data/optimal_minpts_score.rda")
umap_cancertype <- data.table::fread("../data/umap_3d_coors.tsv")
load("../data/kelly.colours.rda")
load("../data/ditto.colours.rda")

>>>>

```{r figure-SM1-plot, fig.width = 9}
load("../data/figure1B_data.rda") ## Load in data processed in figure1.Rmd
load("../data/optimal_minpts_score.rda")
umap_cancertype <- data.table::fread("../data/umap_3d_coors.tsv")
load("../data/kelly.colours.rda")
load("../data/ditto.colours.rda")
